%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}
\usepackage{enumitem}

% FONTS
\usepackage[usenames,dvipsnames]{color}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\usepackage{fontspec}
\setromanfont[Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
\setmonofont[Scale=0.8]{Monaco}
% \setmainfont[Ligatures={Common}, Numbers={OldStyle}, Variant=01,
% BoldFont=LinLibertine_RB.otf}{}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm,
  bookmarks, colorlinks, breaklinks,
% ---- FILL IN HERE THE TITLE AND AUTHOR
    pdftitle={William Mathewson --- Curriculum Vit\ae},
    pdfauthor={William Mathewson},
    pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}

% DOCUMENT
\begin{document}
{\LARGE William Mathewson}\\[1cm]

Phone: \texttt{+44 (0) 7547 155215}\\
Email: \href{mailto:wncmathewson@me.com}{wncmathewson@me.com}\\
%\textsc{url}: \href{http://wncmathewson.me}{http://wncmathewson.me}\\
GitHub: \href{https://github.com/neanias}{https://github.com/neanias}\\
LinkedIn: \href{https://uk.linkedin.com/in/william-mathewson}{https://uk.linkedin.com/in/william-mathewson}

%\hrule
\section*{Work \& Experience}
\noindent

\years{Jun -- Jul 2019} Full Stack Engineer at Edjo Ltd\\
\emph{Built an admin portal using React.js and the Falcon web framework for
  creating new ERC20 tokens on the Ethereum blockchain.}\\
\url{https://edjo.io}\\

\years{Aug 2018 --\\ May 2019} Lead Software Engineer at ThisThat Ltd\\
\emph{Led all engineering activities. This involved:}
\begin{itemize}[noitemsep]
  \item Learning Swift and iOS to lead iOS app development;
  \item Managing the Firebase service;
  \item Designing and building a green-field Python REST backend service,
    written using the Falcon web framework;
  \item Learning many new skills such as SEO, NoSQL databases and deployment
    strategies for GCP and Kubernetes.
\end{itemize}
\url{https://www.thisthatapp.com}\\

\years{Feb 2016 --\\ Jun 2018} Student Developer at Sumdog Ltd\\
\emph{During university, worked as part of the team that maintained the Ruby on
  Rails backend and admin portal. Built a green-field Rails app to run SQL
  queries against multiple servers and tabulate the returned data.}\\
\url{https://www.sumdog.com}\\


\years{Jun -- Jul 2015} Ruby on Rails Developer at Cake Technologies\\
\emph{Worked in the backend development team, maintaining the Ruby on Rails
  backend API during my university summer holiday.}\\
\url{http://www.thecakeapp.com}\\


\years{Jan -- Jul 2014} Ruby on Rails Developer at Wordeo Ltd\\
\emph{Worked in the backend development team, maintaining the Ruby on Rails
  backend API\@. Added functionality to Sinatra-based tools. Wrote Ruby scripts
  to help the marketing department promote the product.}\\


\years{Nov 2013 --\\ Jan 2014} Technical Intern at Wordeo Ltd\\
\emph{Tagged clips in a large video library. Logged and triaged incoming errors
  while tracking down their root causes.}\\


\years{October 2013} Intern at Wordeo Ltd\\
\emph{Worked on tagging clips in a large video library.}\\
\url{http://wordeo.com}


\section*{Relevant Skills}

\subsection*{Programming Languages and Frameworks}

\begin{itemize}[noitemsep]
  \item Python with Falcon and Flask
  \item Ruby and Ruby on Rails
  \item TypeScript and JavaScript
  \item Swift and iOS
\end{itemize}

\emph{Quite competent. Several used for multiple coursework assignments.}
\begin{itemize}[noitemsep]
  \item Java
  \item C
  \item Scala
  \item Haskell
  \item Elixir
\end{itemize}

\subsection*{Development Tools}

\emph{Very competent.}
\begin{itemize}[noitemsep]
  \item PostgreSQL
  \item Firebase
  \item NoSQL
  \item Docker
  \item Kubernetes
  \item Git, GitHub
\end{itemize}

\section*{Leadership Experience}
\noindent


\years{Sept 2015 --\\ May 2016} CompSoc Vice-President (Edinburgh University
Computing Society)\\
\emph{This position involved organising monthly tech talks which involved
  contacting companies and individuals to come and talk to members about
  how/what they do.}\\
\url{https://comp-soc.com}\\


\years{Sept 2015 --\\ May 2018} Officer Cadet in the Edinburgh Universities' Royal
Naval Unit


\section*{Education}
\years{2014--2018} 2:1, BSc (Hons) Computer Science, University of Edinburgh\\


\vfill{}
%\hrulefill

\begin{center}
{\scriptsize %Last updated: \today\- •\-
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{%
\fontspec{Times New Roman}\XeTeX}\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{https://github.com/neanias/CV}{https://github.com/neanias/CV}}
\end{center}

\end{document}

% Local Variables:
% TeX-engine: xetex
% End:
